### 2016-12-06 Manuscript/Figs for Dave.rmd
Figs for Dave

---
output:
  word_document:
    reference_docx: myref.docx
---
```{r setup, include = F}

@@

Fig1A <- ddply(dd,
               .(BirdID),
        mutate,
        nreps = length(RTL)) %>%
  subset(nreps>0) %>%
  subset(!duplicated(paste0(BirdID,Agemonths))) %>%
  ggplot(aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))+
  annotate('text',x = 0,y = 1.7,label = 'A')

@@

Fig1B <- transform(dd,Cohort = factor(LayYear)) %>%
  ggplot(aes(y = RTL,x = Cohort, fill = Cohort))+
  xlab('Birth year') +
  geom_boxplot(outlier.shape = NA) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
        scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.6,label = 'B')

Fig1C <- transform(dd,Cohort = factor(LayYear)) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort,fill = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~log(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
        scale_fill_manual(values = c15)+
  annotate('text',x = 0,y = 1.3,label = 'C')

  Fig1D <- ggplot(dd3, aes(x = DeltaLogAge,y = RTL))+
  geom_point(alpha = 1,col='grey')+
  xlab(expression(Delta*'Log age (years)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',method = 'lm')+
  annotate('text',x = -1.5,y = 1.7,label = 'D')

pdf('Figures/Figure 1.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig1A,Fig1B,Fig1C,Fig1D,layout = matrix(1:4,2,2,byrow = T))
dev.off()

@@

```{r Figure 2}

Fig2A <- ggplot(dd3,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2) +
  annotate('text',x = 0.3,y = 1.7,label = 'A')

Fig2B <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2) +
  annotate('text',x = -1,y = 1,label = 'B')

pdf('Figures/Figure 2.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B)
dev.off()

```{r Figure 3}

RTL_Full2 <- standardize(RTL_Full)

CIs <- CIwald(RTL_Full2)
t1a <- data.frame(myx = row.names(CIs)[7:nrow(CIs)],
                  Estimate = fixef(RTL_Full2),
                  X2.5. = CIs[7:nrow(CIs),1],
                  X97.5. = CIs[7:nrow(CIs),2],
                  row.names = NULL,
                  stringsAsFactors = F)

nams <- t1a$myx
nams[nams == 'z.LogAge'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus length'
nams[nams == 'c.Helper'] <- 'Number helpers'
nams[nams == 'z.GroupSize'] <- 'Group size'
nams[nams == 'c.Sex'] <- 'Sex (males)'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Insect'] <- 'Insect abundance'
nams[nams == 'z.TQ'] <- 'Territory quality'
nams[nams == 'z.Density'] <- 'Density'

t1a$myx <- nams

t1a$myx <- factor(t1a$myx,levels = t1a$myx[order(t1a$Estimate,decreasing = T)])
t1a <- subset(t1a,myx != "(Intercept)")

Fig3A <- forestplot(t1a,RI = F)+
  annotate('text',y = 0.1,x = 0.6,label = 'A')

Fig3B <- ggplot(dd,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm') +
  scale_color_manual(values = c('gold2','red'))+
  annotate('text',x = 17,y = 1.7,label = 'B')

Fig3C <- ggplot(dd,
       aes(y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey') +
  annotate('text',x = 2.5,y = 1.6,label = 'C')

pdf('Figures/Figure 3.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig3A,Fig3B,Fig3C,layout = matrix(c(1,1,2,3),byrow = T,nrow = 2))
dev.off()

>>>>

---
  output:
  word_document:
  reference_docx: myref.docx
---

```{r setup, include = F}

@@

pdf('Figures/Figures for Dave NERC grant.pdf',
    width = 5,
    height = 5,
    paper = 'a4')

@@

transform(dd,Cohort = factor(LayYear)) %>%
  ddply(.(LayYear),
        summarise,
        meanRTL = mean(RTL),
        seRTL = se(RTL)) %>%
  ggplot(aes(y = meanRTL,x = LayYear))+
  xlab('Birth year') +
  ylab('RTL')+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymax = meanRTL+seRTL,ymin=meanRTL-seRTL),width =0.2)+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  scale_fill_manual(values = c15)

transform(dd,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2001,2005,2010)) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort,fill = Cohort))+
  xlab('Age (years)') +
  xlim(c(0,6))+
  geom_smooth(method = 'lm', formula = y~log(x),se = T,fullrange=T,alpha = 0.1) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  scale_color_manual(values = c15)+
  scale_fill_manual(values = c15)

ddply(dd,
      .(Insect),
      summarise,
      meanRTL = mean(RTL),
      seRTL = se(RTL)) %>%
ggplot(aes(y = meanRTL,
              x=Insect)) +
  ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_point()+
  geom_errorbar(aes(ymin=meanRTL-seRTL,ymax=meanRTL+seRTL))+
  stat_smooth(method = 'lm',col = 'darkgrey')

dev.off()

@@
